Who are Toronto’s Crime Victims? A Gender and Crime Type Analysis from 2014 to 2023

### 2024-09-27 paper/paper.qmd
Updated graph headers for consistency

---
title: "Who are Toronto’s Crime Victims? A Gender and Crime Type Analysis from 2014 to 2023"
author: 
  - Kevin Roe
thanks: "All data, R code, and other files are available in the following GitHub repository: <https://github.com/Kanghyunroe/victims_of_crimes/tree/master>"
date: today
date-format: long
abstract: "This paper analyzes data from the Toronto Police Service's Annual Statistical Report on Crime Victims from 2014 to 2023, focusing on the relationship between sex and crime victimization in the city. Overall, male victims outnumber female victims by 2%, but women are disproportionately affected in certain crime categories: female victims outnumber males by 78% in sexual crimes and by 9% in other crimes. These findings highlight how vulnerability to certain crimes is influenced by sex, underscoring the need for targeted policy initiatives to strengthen victim support services. Further research should focus on victims of fatal crimes, particularly those linked to Intimate Partner Violence (IPV) to address the limitations of the dataset."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

#### First Graph ####
ggplot(summary, aes(x = Sex, y = Victims_of_Crimes, fill = Sex)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = Victims_of_Crimes),
            position = position_dodge(width = 0.9),
            vjust = -0.2,
            size = 3.5) +
  labs(x = "Sex",
       y = "Victims of Crimes") +
  scale_y_continuous(labels = comma) +
  theme_classic()

>>>>

---
title: "Who are Toronto’s Crime Victims? A Gender and Crime Type Analysis from 2014 to 2023"
author: 
  - Kevin Roe
thanks: "All data, R code, and other files are available in the following GitHub repository: <https://github.com/Kanghyunroe/victims_of_crimes/tree/master>"
date: 09-27-2024
date-format: long
abstract: "This paper analyzes data from the Toronto Police Service's Annual Statistical Report on Crime Victims from 2014 to 2023, focusing on the relationship between sex and crime victimization in the city. Overall, male victims outnumber female victims by 2%, but women are disproportionately affected in certain crime categories: female victims outnumber males by 78% in sexual crimes and by 9% in other crimes. These findings highlight how vulnerability to certain crimes is influenced by sex, underscoring the need for targeted policy initiatives to strengthen victim support services. Further research should focus on victims of fatal crimes, particularly those linked to Intimate Partner Violence (IPV) to address the limitations of the dataset."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

#### First Graph ####
ggplot(summary, aes(x = Sex, y = Victims_of_Crimes, fill = Sex)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = Victims_of_Crimes),
            position = position_dodge(width = 0.9),
            vjust = -0.2,
            size = 3.5) +
  labs(x = "Sex",
       y = "Number of Victims") +
  scale_y_continuous(labels = comma) +
  theme_classic()
